Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Better statement of purpose in abstract, mentions limited to axis-aligned volumes

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is difficult because the renderer must alternate
between sampling from each volume to achieve the correct blending.  Methods for
rendering an arbitrary number of intersecting volumes on the GPU have been
developed, but they can require a large amount of geometry to be created every
frame, or may be difficult or time-consuming to implement.  This paper
investigates implementing the simplest case, where two volumes overlap, using
familiar boolean operations and a traditional graphics library.
\end{abstract}

>>>>

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is difficult because the renderer must alternate
between sampling from each volume to achieve the correct blending.  Methods for
rendering an arbitrary number of intersecting volumes on the GPU have been
developed, but they can require a large amount of geometry to be created every
frame, or may be difficult or time-consuming to implement.  This paper
investigates whether using familiar Boolean operations may be faster or easy to
implement in the simple case where two axis-aligned volumes intersect.
\end{abstract}
